What is disputed on the web?

### 2010-01-29 papers/wicow_claimfinder/claimfinder.tex
Improved filter rules. Fleshed out paper text more. Merged related work

\documentclass{acm_proc_article-sp}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\newcommand{\want}[1]{}
\newcommand{\idea}[1]{}
\newcommand{\note}[1]{}

% Mark up a point that we want to flesh out into more text
\newcommand{\x}[1]{{\color{blue} #1}\\}

% Mark up some work that we need to do in order for this paper to be telling the truth
\newcommand{\todo}[1]{{\color{red} #1}\\}

\newcommand{\maybe}[1]{}

@@

Given a corpus of disputed claims $S$, we can identify other patterns that suggest that a claim is disputed by searching the web for contexts in which known disputed claims appear. This is an instance of the distributional hypothesis~\cite{distributional-hypothesis}, which theorises that if a pattern occurs with similar phrases filling its slots (it is distributionally similar) then it has a similar meaning.

@@

\x{Cite Pew study on this? Cite other people talking about misinformation}.

@@

Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content. For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{wikitrust} identifies potentially unreliable sections of an article by analyzing its edit history. Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos. Fogg et al~\cite{Fogg} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing. Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction. AuContraire~\cite{Ritter2008} uses TextRunner~\cite{Banko2007} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

@@

\input{relatedwork.tex}

@@

@@

We search the web for patterns that indicate that a claim is disputed. Figure~\ref{templates} shows a subset of the patterns that we search for. For each pattern, we show the number of times that Google estimates that the pattern appears on the web.

@@

Not every chunk of text identified by one of our patterns is a well-formed disputed claim. Consider for example the text chunks in Figure~\ref{filtered}.

We use a simple natural language parser to filter the chunks of text that match our patterns.

We pass each such chunk of raw text to a natural language parser (custom grammar, and an NLTK~\cite{nltk} regexp parser). We throw away any chunk of text that does not appear to be a statement, or which uses a referent (such as ``it'' or ``he'') that cannot be easily resolved. Figure~\ref{filtered} shows examples of phrases that we filter.

\begin{figure*}[t]
\begin{tabular}{|l|l|l|}
  \hline
  {\bf extracted text} & {\bf accepted} & {\bf reason} \\
  \hline
  {\it the false claim that} won't go away & reject & ``wont go away'' is not a statement \\
  {\it falsely claimed that} he didn't do it & reject & ``he'' and ``it'' are unbound referents \\ 
  {\it wrongly believe that} the moon is made of cheese & accept & \\
  {\it false claim that} Elvis is alive despite all evidence & \\
  \hline
\end{tabular}
\label{filtered}
\caption{We filter out text that does not look like a statement}

\todo{Our parser is currently a bit rubbish. Need to work out how to do this properly.}
\todo{We need to use the correct terminology here.}

\x{Remove anything containing stuff like 'if'}
\x{Disallow possesives like its/his etc unless a noun has come first}
\x{Strip HTML tags}

@@

@@

\begin{figure}[tb]
  \begin{tabular}{|ll|}
    \hline
    {\bf Google Count\footnotemark} & {\bf Template}\\ 
    \hline
    \multicolumn{2}{|c|}{\it Something that could be challenged}\\
    163,000,000 & believe that \\
    206,000,000 & think that \\
    49,500,000 & idea that \\
    33,600,000 & claim that \\
   \hline
   \multicolumn{2}{|c|}{\it Something others believe}\\
    120,000,000 & the belief that \\
    49,000,000 & who believe that \\
    50,500,000 & who think that \\
    10,100,000 & believing that \\
    9,430,000 & claiming that \\
    \hline
    \multicolumn{2}{|c|}{\it Something false}\\
    243,000,000 & it is not the case that \\
    30,700,000 & it is not true that \\
    15,600,000 & the misconception that \\
    13,000,000 & the delusion that \\
    12,400,000 & the myth that \\
    9,960,000 & into believing that \\
    8,970,000 & disagree with the claim that \\
    7,190,000 & the mistaken belief that \\
    6,160,000 & disagree with the assertion that \\
    4,950,000 & the fallacy that \\
    3,720,000 & the lie that \\
    3,700,000 & mistaken belief that \\
    3,600,000 & the false belief that \\
    3,440,000 & the deceit that \\
    2,290,000 & cast doubt on the claim that \\
    2,140,000 & the deception that \\
    1,760,000 & the misunderstanding that \\
    1,630,000 & mistakenly believe that \\
    1,090,000 & false claim is that \\
    1,290,000 & the hoax that \\
    698,000 & absurdity of the claim that \\
    681,000 & falsely claimed that \\
    659,000 & no longer think that \\
%     654,000 & urban legend that \\
%     530,000 & the absurd idea that \\
%     373,000 & erroneously believe that \\
%     334,000 & the fabrication that \\
%     103,000 & falsely claiming that \\
%     140,000 & erroneous belief that \\
%     72,600 & falsely claim that \\
%     152,000 & bogus claim that \\
%     224,000 & the fantasy that \\
%     171,000 & incorrectly claim that \\
%     249,000 & incorrectly claimed that \\
%     232,000 & incorrectly believe that \\
%     98,900 & stupidly believe that \\
%     429,000 & falsely believe that \\
%     376,000 & wrongly believe that \\
%     189,000 & falsely suggests that \\
%     280,000 & falsely claims that \\
%     148,000 & false claim that \\
%     136,000 & no longer believe that \\
%     65,300 & urban myth that \\
%     59,500 & falsely stated that \\
    \hline
  \end{tabular}
  \label{templates}
  \caption{Some of the templates that we use to search for disputed claims, and Google's rough estimate of how many times each one appears on the web}

\end{figure}

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\newcommand{\want}[1]{}
\newcommand{\idea}[1]{}
\newcommand{\note}[1]{}
\newcommand{\x}[1]{}
\newcommand{\todo}[1]{}
\newcommand{\maybe}[1]{}

% Mark up a point that we want to flesh out into more text
%\newcommand{\x}[1]{{\color{blue} #1}\\}

% Mark up some work that we need to do in order for this paper to be telling the truth
%\newcommand{\todo}[1]{{\color{red} #1}\\}

%\newcommand{\maybe}[1]{}

@@

Given a corpus of disputed claims $S$, we can identify other patterns that suggest that a claim is disputed by searching the web for contexts in which known disputed claims appear. This is an instance of the distributional hypothesis~\cite{Harris1954,Systems2000}, which theorises that if a pattern occurs with similar phrases filling its slots (it is distributionally similar) then it has a similar meaning.

@@

\x{Cite Pew study on this? Cite other people talking about misinformation.}

@@

Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content. For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{wikitrust} identifies potentially unreliable sections of an article by analyzing its edit history. Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos. Fogg et al~\cite{Fogg2003} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing. Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction. AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

@@

This work is also closely related to the NLP areas of opinion mining and/or sentiment analysis, 
textual entailment and contradiction detection. Sentiment analysis aims to determine the attitude 
(usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}. 
Textual entailment is the task of deciding, given two text fragments, whether the meaning of one 
text can be inferred from the other text (add references).

% I think I've folded the stuff from this file into the main body now
%\input{relatedwork.tex}

@@

\begin{figure*}[tb]
\begin{center}
\begin{tabular}{|l|l|l|l|}
  \hline
  & {\bf extracted text} & {\bf valid} & {\bf details} \\
  \hline
  1. & the false claim that {\it won't go away} & no & ``wont go away'' is not a statement \\
  2. & falsely claimed that {\it he didn't do it} & no & ``he'' and ``it'' are unbound referents \\
  3. & falsely claimed that {\it federal labor laws do not apply} & no & object of the verb is not present\\
  4. & false claim that {\it Elvis is alive} despite all evidence & yes & but drop everything after ``despite''\\
  5. & wrongly believe that {\it the moon is made of cheese} & yes & it is a statement about the world \\
\hline
\end{tabular}
\end{center}
\label{filtered}
\caption{We filter out text that does not look like a statement}

@@

We search the web for patterns that indicate that a claim is disputed, such as ``false claim that $X$'' or or ``it is not true that $X$''. Figure~\ref{templates} shows a subset of the patterns that we search for. For each pattern, we show the number of times that Google estimates that the pattern appears on the web.

This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.

@@

Not every chunk of text identified by one of our patterns is a well-formed disputed claim. Consider for example the text chunks in Figure~\ref{filtered}. A chunk of text might not be a statement (case 1), it might include unbound referents such is ``it'', or ``they'' (case 2), or it might only make sense within the context of a particular document (case 3).

We use a simple filter that looks for cases 1 and 2, but does not yet deal with case 3. We use the part-of-speech tagger from NLTK~\cite{nltk}, and then use a simple regexp parser to apply a series of simple rules.

\begin{enumerate}
\item To ensure that the text represent a real statement (case 1) we accept only text that contains either two noun phrases (e.g. ``{\it George Bush} is from {\it Texas}''), or a noun phrase and an adjective (e.g. ``{\it Cocaine} is {\it addictive}''). We do not accept text that contains merely a noun and a verb (e.g. ``{\it Federal laws} do not {\it apply}'') since manual inspection of our data set suggests that in such phrases the verb typically refers to a noun that is defined outside the statement itself.

\item We also discard any statement that contains a personal pronoun such as ``he'', ``she'', ``it'', or ``they'' unless it is proceeded by a noun (addressing case 2). We allow a personal pronoun after a noun, since manual inspection suggests that in most cases the personal pronoun refers to the noun, for example ``Bill Clinton said he wants to slow down the economy''. While we could in theory resolve other references, this is known to be a hard problem, and we have access to a large enough set of candidate claims that we can afford to throw away claims that are not easy for us to process.

\item In some cases a disputed claim will be followed by information about where the claim was made, or why the claim is wrong. For example ``he claimed that the moon was made of cheese {\it on his show}'' or ``he claimed that the moon is made of cheese {\it despite contrary evidence}''. We chop off such suffixes by discarding any text that follows a word such as ``despite'', ``however'', ``but'', or ``was''.
\end{enumerate}

These rules were crafted by hand, based on trial and error and manual inspection of a relatively small number of claims. In the future we would like to use a more rigorous statistical method to produce more sophisticated rules for selecting high quality disputed claims, guided by a larger hand-annotated data set. We are also considering adopting an external framework such as TextRunner~\cite{Etzioni2008,Banko2008}.

\todo{Need a rough evaluation of what proportion of claims get thrown away by each rule, and how accurate these rules are.}

@@

Rather that searching for an arbitrary collection of known disputed claims, we found that we generated better templates by searching for claims that most documents disagee with (e.g. ``eskimos have many words for snow'') rather than claims that many people agree with (e.g. ``there is a God''). If many people agree with a claim is true then many of the patterns that we find will not be patterns that indicate that the claim is disputed. Even when we search for claims that are highly disputed, our algorithm still finds many patterns that do not indicate dispute. We thus rely on a human to pick which prefixes to use.

We also find that we get higher quality results if we limit ourselves to prefixes that end in ``that''. For example, if we search for ``that eskimos have many words for snow'' then most prefixes we find do indeed indicate dispute, however if we just search for ``eskimos have many words for snow'' then we get a much lower hit rate.

This approach is an example of the Distributional Hypothesis. The distributional hypothesis, as originally framed~\cite{Harris1954,Systems2000}, theorised that words that appear in similar contexts have similar meanings. This has more recently been extended to patterns. If two patterns appear in a corpus with similar text filling their slots, then it is likely that the patterns have similar meanings. DIRT~\cite{Lin2001} discovers inference rules such as (``$X$ is author of $Y$'' $\equv$ ``$X$ wrote $Y$'') by looking for patterns that have a similar distribution of text filling their slots. Pasca and Dienes~\cite{Pasca2005} detect paraphrases on the web by searching for text fragments that appear in similar contexts on web pages.

@@

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|ll|}
    \hline
    {\bf Google Count\footnotemark} & {\bf Template}\\ 
    \hline
    \multicolumn{2}{|c|}{\it Something that could be challenged}\\
    163,000,000 & believe that \\
    206,000,000 & think that \\
    49,500,000 & idea that \\
    33,600,000 & claim that \\
   \hline
   \multicolumn{2}{|c|}{\it Something others believe}\\
    120,000,000 & the belief that \\
    49,000,000 & who believe that \\
    50,500,000 & who think that \\
    10,100,000 & believing that \\
    9,430,000 & claiming that \\
    \hline
    \multicolumn{2}{|c|}{\it Something false}\\
    243,000,000 & it is not the case that \\
    30,700,000 & it is not true that \\
    15,600,000 & the misconception that \\
    13,000,000 & the delusion that \\
    12,400,000 & the myth that \\
    9,960,000 & into believing that \\
    8,970,000 & disagree with the claim that \\
    7,190,000 & the mistaken belief that \\
    6,160,000 & disagree with the assertion that \\
    4,950,000 & the fallacy that \\
    3,720,000 & the lie that \\
    3,700,000 & mistaken belief that \\
    3,600,000 & the false belief that \\
    3,440,000 & the deceit that \\
    2,290,000 & cast doubt on the claim that \\
    2,140,000 & the deception that \\
    1,760,000 & the misunderstanding that \\
    1,630,000 & mistakenly believe that \\
    1,090,000 & false claim is that \\
    1,290,000 & the hoax that \\
    698,000 & absurdity of the claim that \\
    681,000 & falsely claimed that \\
    659,000 & no longer think that \\
%     654,000 & urban legend that \\
%     530,000 & the absurd idea that \\
%     373,000 & erroneously believe that \\
%     334,000 & the fabrication that \\
%     103,000 & falsely claiming that \\
%     140,000 & erroneous belief that \\
%     72,600 & falsely claim that \\
%     152,000 & bogus claim that \\
%     224,000 & the fantasy that \\
%     171,000 & incorrectly claim that \\
%     249,000 & incorrectly claimed that \\
%     232,000 & incorrectly believe that \\
%     98,900 & stupidly believe that \\
%     429,000 & falsely believe that \\
%     376,000 & wrongly believe that \\
%     189,000 & falsely suggests that \\
%     280,000 & falsely claims that \\
%     148,000 & false claim that \\
%     136,000 & no longer believe that \\
%     65,300 & urban myth that \\
%     59,500 & falsely stated that \\
    \hline
  \end{tabular}
  \label{templates}
  \caption{Some of the templates that we use to search for disputed claims, and Google's rough estimate of how many times each one appears on the web}
\end{center}
\end{figure}

### 2010-01-29 papers/wicow_claimfinder/relatedwork.tex
Improved filter rules. Fleshed out paper text more. Merged related work

The automatic analysis of text falls into the field of natural language processing (NLP) 
and the problems and methods described here draw from a variety of sub-areas within the NLP literature. 
The method described in Section~\ref{sec:XX} that uses a set of XX extraction patterns to generate 
candidate claims  is inspired by \cite{Hearst92} and is an instance of template inference (aka pattern matching) 
that has been used extensively for several NLP task (for example \cite{Riloff93}, \cite{Jones99} and 
\cite{etzioni05} for information extraction). {\bf XX DESCRIBE SIMILARITIES AND DIFFENRENCES}.

>>>>

The automatic analysis of text falls into the field of natural language processing (NLP) 
and the problems and methods described here draw from a variety of sub-areas within the NLP literature. 
The method described in Section~\ref{sec:XX} that uses a set of XX extraction patterns to generate 
candidate claims  is inspired by \cite{Hearst1992} and is an instance of template inference (aka pattern matching) 
that has been used extensively for several NLP task (for example \cite{Riloff93}, \cite{Jones99} and 
\cite{etzioni05} for information extraction). {\bf XX DESCRIBE SIMILARITIES AND DIFFENRENCES}.
